---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(repos = c(CRAN = "https://cran.r-project.org"))
```

# testproject

The `testproject` package is designed to streamline the analysis of survey and experimental data, with a specific focus on demographic and quality-of-life surveys. It includes tools for data cleaning, transformation, visualization, and summarization, making it easier for researchers and statisticians to extract meaningful insights from complex survey datasets.

## Background

Survey data often requires significant preprocessing and analysis to uncover actionable insights. This package was developed to simplify these tasks, with built-in functions to:
- Convert categorical survey responses into numeric formats for analysis.
- Generate customizable visualizations to explore relationships within data.
- Summarize survey results using proportion tables and counts.

The package's primary dataset, `asian_american`, provides an example of a well-structured survey dataset, sourced from the [City of Austin Open Data Portal](https://data.austintexas.gov). This dataset focuses on quality-of-life factors among Asian American populations, including demographic, social, and emotional well-being data.


## Installation
You can install this package from GitHub:
```{r}
install.packages("devtools")
devtools::install_github("viivnguyen/testproject")
```

## Examples
### Example 1: Convert Survey Responses to Numeric Levels
Easily transform categorical survey responses into numeric formats for modeling or analysis.

```{r}
library(Stat108Project2)

data <- data.frame(proficiency = c("Well", "Not at all", NA, "Not well", "Very well"))
response_scale <- c("Not at all", "Not well", "Well", "Very well")

data <- surveylevels(data, column = "proficiency", ordered_levels = response_scale)
print(data)
```

### Example 2: Summarize Survey Data
Create a proportion table to analyze the distribution of responses across categories.

```{r}
proptable(asian_american,
          x = "education",
          y = "english_speaking",
          include_total = TRUE)
```

### Example 3: Visualize Survey Data
Generate a scatter plot to explore relationships within the dataset.

```{r}
scatter(asian_american,
        x = "age",
        y = "income",
        color = "education",
        title = "Income by Age and Education Level",
        xlab = "Age (years)",
        ylab = "Income",
        add_trendline = TRUE)
```

## Features
- Data Conversion: Seamlessly convert survey responses into numeric formats.
- Summarization: Quickly create proportion tables for categorical variables.
- Visualization: Generate detailed and customizable scatter plots.
For more detailed documentation, please refer to the package vignette.

## Citation
The dataset used in this package is sourced from the City of Austin Open Data Portal.
